### 2022-06-06 main/chapter_2ljets.tex
add illustrative presel plots; minor tidyup

\begin{table}[tp]
\centering
\begin{tabular}{c}
Preselection:
\\[1em]
$n_\mathrm{leptons}^\mathrm{signal} = n_\mathrm{leptons}^\mathrm{baseline} = 2$
\\[0.5em]
same flavour, opposite charge leptons
\\[0.5em]
$\njet \geq 1$
\\[0.5em]
$p_\mathrm{T}^{\,\ell_2} > 25$
\\[0.5em]
$\met > 100$
\\[0.5em]
$\metsig > 6$
\end{tabular}
\caption{%
`Preselection' requirements ensured prior to all region definitions in the
$\twoljets$-electroweak search.
}
\label{tab:2ljets_presel}
\end{table}

@@

\begin{table}[tp]
\centering
\begin{tabular}{lccccc}
& $\njet$
& $\nbtag$
& $\metsig$
& $m_*$
& $\rjj$
\\[1em]
SR-High
& $\geq2$
& $\leq 1$
& $18\textrm{--}21\textrm{--}\infty$
& $\mjj\!:~  60\textrm{--}110$
& $0\textrm{--}0.8\textrm{--}1.6$
\\[0.5em]
\: VR-High
& $\geq2$
& $\leq 1$
& $> 18$
& $\uwave{\mjj\!:~  20\textrm{--}60 \mid 60\textrm{--}110}$
& $< 1.6$
\\[0.5em]
\: VR-High-R
& $\geq 2$
& $\leq 1$
& $> 18$
& $\uwave{\mjj\!:~  > 20}$
& $\uwave{> 1.6}$
\\[1em]
SR-High-1J
& $\hphantom{\geq}~1$
& $\leq 1$
& $> 12$
& $\mjetone\!:~  60\textrm{--}110$
&
\\[0.5em]
\: VR-High-1J
& $\hphantom{\geq}~1$
& $\leq 1$
& $> 12$
& $\uwave{\mjetone\!:~  20\textrm{--}60 \mid 60\textrm{--}110}$
&
\\[1em]
SR-$\llbb$
& $\geq 2$
& $\geq 2$
& $> 18$
& $\mbb\!:~  60\textrm{--}150$
&
\\[0.5em]
\: VR-$\llbb$
& $\geq 2$
& $\geq 2$
& $\uwave{12\textrm{--}18}$
& $\mbb\!:~  60\textrm{--}150$
&
\end{tabular}
\\[1em]
Common: Preselection,
$\mll \in 71\textrm{--}111$, and
$\mttwoll > 80$.
\caption[
High region definitions in the $\twoljets$-electroweak analysis
]{%
High region definitions in the $\twoljets$-electroweak analysis.
En-dashes `$a\textrm{--}b$' indicate open intervals $(a, b)$.
Concatenated intervals `$a\textrm{--}b\textrm{--}c$' indicate binning
with boundaries at $a$, $b$, and $c$.
The mid bar `$\mid$' indicates logical or.
Differences between regions are \uwave{underlined}.
}
\label{tab:2ljets_high}
\end{table}

@@

\begin{table}[tp]
\centering
\begin{tabular}{lccccc}
& $\njet$
& $\nbtag$
& $\metsig$
& $\mjj$
& $\ptjone$
\\[1em]
SR-Int
& $\geq 2$
& $\hphantom{\geq}~0$
& $12\textrm{--}15\textrm{--}18$
& $60\textrm{--}110$
& $> 60$
\\[0.5em]
\: VR-Int
& $\geq 2$
& $\hphantom{\geq}~0$
& $12\textrm{--}18$
& $60\textrm{--}110$
& $\uwave{< 60}$
\\[1em]
CR-VZ
& $\geq 2$
& $\hphantom{\geq}~0$
& $12\textrm{--}18$
& $\uwave{20\textrm{--}60 \mid 60\textrm{--}110}$
& $\uwave{\hphantom{< 60}}$
\\[0.5em]
CR-tt
& $\geq 2$
& $\uwave{\geq 1}$
& $\uwave{9\textrm{--}12}$
& $\uwave{20}$
& $> 60$
\end{tabular}
\\[1em]
Common: Preselection,
$\njet \geq 2$,
$\mll \in 81\textrm{--}101$, and
$\mttwoll > 80$.
\caption[
Intermediate region definitions in the $\twoljets$-electroweak analysis
]{%
Intermediate region definitions in the $\twoljets$-electroweak analysis.
En-dashes `$a\textrm{--}b$' indicate open intervals $(a, b)$.
Concatenated intervals `$a\textrm{--}b\textrm{--}c$' indicate binning
with boundaries at $a$, $b$, and $c$.
The mid bar `$\mid$' indicates logical or.
Differences between regions are \uwave{underlined}.
}
\label{tab:2ljets_int}
\end{table}

@@

\begin{table}[tp]
\centering
\begin{tabular}{lcccccccc}
& $\metsig$
& $\mjj$
& $\mttwoll$
& $\rll$
& $\dphillmet$
\\[1em]
SR-Low
& $6\textrm{--}9\textrm{--}12$
& $60\textrm{--}110$
& $> 80$
& $< 1$
&
\\[0.5em]
\: VR-Low
& $6\textrm{--}12$
& $60\textrm{--}110$
& $>80$
& $\uwave{1\textrm{--}1.4}$
&
\\[1em]
SR-Low-2
& $6\textrm{--}9$
& $60\textrm{--}110$
& $< 80$
& $< 1.6$
& $< 0.6$
\\[0.5em]
\: VR-Low-2
& $6\textrm{--}9$
& $\uwave{20\textrm{--}60 \mid 60\textrm{--}110}$
& $< 80$
& $< 1.6$
& $< 0.6$
\\[1em]
CR-Z
& $6\textrm{--}9$
& $\uwave{20\textrm{--}60 \mid 60\textrm{--}110}$
& $> 80$
& $\uwave{\hphantom{< 1.6}}$
& $\uwave{\hphantom{< 0.6}}$
\end{tabular}
\\[1em]
Common: Preselection,
$\njet = 2$,
$\nbtag = 0$, and
$\mll \in 81\textrm{--}101$.
\caption[
Low region definitions in the $\twoljets$-electroweak analysis
]{%
Low region definitions in the $\twoljets$-electroweak analysis.
En-dashes `$a\textrm{--}b$' indicate open intervals $(a, b)$.
Concatenated intervals `$a\textrm{--}b\textrm{--}c$' indicate binning
with boundaries at $a$, $b$, and $c$.
The mid bar `$\mid$' indicates logical or.
Differences between regions are \uwave{underlined}.
}
\label{tab:2ljets_low}
\end{table}

@@

\begin{table}[tp]
\centering
\begin{tabular}{lccccc}
& $\metsig$
& $\mll$
& $\mttwoll$
& $\ptjone$
& $\dphijmet$
\\[1em]
SR-OffShell
& $>9$
& $12\textrm{--}40\textrm{--}71$
& $>100$
& $>100$
& $>2$
\\[0.5em]
\: VR-OffShell
& $>9$
&  12--71
& $\uwave{80\textrm{--}100}$
& $> 100$
& $> 2$
\\[1em]
CR-DY
& $\uwave{6\textrm{--}9}$
& $12\textrm{--}71$
& $> 100$
& $\uwave{\hphantom{> 100}}$
& $\uwave{\hphantom{> 2}}$
\end{tabular}
\\[1em]
Common: Preselection,
$\njet \geq 2$, and
$\nbtag = 0$.
\caption[
Off-shell region definitions in the $\twoljets$-electroweak analysis
]{%
Off-shell region definitions in the $\twoljets$-electroweak analysis.
En-dashes `$a\textrm{--}b$' indicate open intervals $(a, b)$.
Concatenated intervals `$a\textrm{--}b\textrm{--}c$' indicate binning
with boundaries at $a$, $b$, and $c$.
The mid bar `$\mid$' indicates logical or.
Differences between regions are \uwave{underlined}.
}
\label{tab:2ljets_offshell}
\end{table}

@@

\begin{figure}[tp]
\centering
\begin{subfigure}{0.9\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_low_mjj_SRLow_or_CRZ_mg5.pdf}
\caption{}
\end{subfigure}
\caption[
The union of CR-Z and SR-Low with an alternative $\zjets$ simulation using
MadGraph
]{%
The union of CR-Z and SR-Low with an alternative $\zjets$ simulation using
MadGraph.
This sample has reduced statistical precision, decreased yields in the signal
region, and increased yields (which match data better) in the high-$\mjj$
overflow bin.
}
\label{fig:2ljets_low_sr_or_cr_region_alt}
\end{figure}

\begin{figure}[tp]
\centering
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_aux_CR_Z_EWKSR_Low_EWK_mjj_no_sr.png}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_aux_CR_Z_EWKSR_Low_EWK_mjj.pdf}
\caption{}
\end{subfigure}
\caption[
Distribution of $\mjj$ in CR-Z and SR-Low with all systematic variations
]{%
Distribution of $\mjj$ in CR-Z and SR-Low with all systematic variations
(a) fitted to control regions, and (b) fitted to control and signal regions.
The arrows point in to the signal region, which shows a large peak in the
diboson background near $m(W)$.
Auxiliary materials to the paper~\cite{atlas2022searches} include (b), in which
the $\zjets$ background in SR-Low has been collapsed to fit the deficit.
Pre-fit yields are presented in Figures~\ref{fig:2ljets_low_sr_or_cr_region}
and~\ref{fig:2ljets_low_sr_or_cr_region_alt}.
}
\label{fig:2ljets_low_crz_pre_post}
\end{figure}

\begin{figure}[tp]
\centering
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_vrlow_met_Sign_VRLow.pdf}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_vrlow_met_Sign_VRLow_mg5.pdf}
\caption{}
\end{subfigure}
\caption[
Pre-fit yields in VR-Low with standard and alternative $\zjets$ simulations
]{%
Pre-fit yields in VR-Low with (a) standard and (b) alternative $\zjets$
simulations.
Errors are statistical.
}
\label{fig:2ljets_vrlow_alt}
\end{figure}

\begin{figure}[tp]
\centering
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_prefit_VR_Low_EWK_met_Sign_no_sr.png}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_postfit_VR_Low_EWK_met_Sign.pdf}
\caption{}
\end{subfigure}
\caption[
Comparison of VR-Low before and after fitting to the signal regions
]{%
Comparison of VR-Low (a) before and (b) after fitting to the signal regions.
All systematic variations are included after fitting to the control regions.
The signal region deficit pulls the $\zjets$ below data in the validation
region, whose likelihood is not included in the \heplikelihood.
Figure (b) is reproduced from paper~\cite{atlas2022searches}.
Each last bin includes overflow.
}
\label{fig:2ljets_low_vrlow_pre_post}
\end{figure}

>>>>

\begin{table}[tp]
\centering
\begin{tabular}{c}
Pre-selection:
\\[1em]
$n_\mathrm{leptons}^\mathrm{signal} = n_\mathrm{leptons}^\mathrm{baseline} = 2$
\\[0.5em]
same flavour, opposite charge leptons
\\[0.5em]
$\njet \geq 1$
\\[0.5em]
$p_\mathrm{T}^{\,\ell_2} > 25$
\\[0.5em]
$\met > 100$
\\[0.5em]
$\metsig > 6$
\end{tabular}
\caption{%
`Pre-selection' requirements ensured prior to all region definitions in the
$\twoljets$-electroweak search.
}
\label{tab:2ljets_presel}
\end{table}

@@

\begin{table}[tp]
\centering
\begin{tabular}{lccccc}
& $\njet$
& $\nbtag$
& $\metsig$
& $m_*$
& $\rjj$
\\[1em]
SR-High
& $\geq2$
& $\leq 1$
& $18\textrm{--}21\textrm{--}\infty$
& $\mjj\!:~  60\textrm{--}110$
& $0\textrm{--}0.8\textrm{--}1.6$
\\[0.5em]
\: VR-High
& $\geq2$
& $\leq 1$
& $> 18$
& $\uwave{\mjj\!:~  20\textrm{--}60 \mid 60\textrm{--}110}$
& $< 1.6$
\\[0.5em]
\: VR-High-R
& $\geq 2$
& $\leq 1$
& $> 18$
& $\uwave{\mjj\!:~  > 20}$
& $\uwave{> 1.6}$
\\[1em]
SR-High-1J
& $\hphantom{\geq}~1$
& $\leq 1$
& $> 12$
& $\mjetone\!:~  60\textrm{--}110$
&
\\[0.5em]
\: VR-High-1J
& $\hphantom{\geq}~1$
& $\leq 1$
& $> 12$
& $\uwave{\mjetone\!:~  20\textrm{--}60 \mid 60\textrm{--}110}$
&
\\[1em]
SR-$\llbb$
& $\geq 2$
& $\geq 2$
& $> 18$
& $\mbb\!:~  60\textrm{--}150$
&
\\[0.5em]
\: VR-$\llbb$
& $\geq 2$
& $\geq 2$
& $\uwave{12\textrm{--}18}$
& $\mbb\!:~  60\textrm{--}150$
&
\end{tabular}
\\[1em]
Common: Pre-selection,
$\mll \in 71\textrm{--}111$, and
$\mttwoll > 80$.
\caption[
High region definitions in the $\twoljets$-electroweak analysis
]{%
High region definitions in the $\twoljets$-electroweak analysis.
En-dashes `$a\textrm{--}b$' indicate open intervals $(a, b)$.
Concatenated intervals `$a\textrm{--}b\textrm{--}c$' indicate binning
with boundaries at $a$, $b$, and $c$.
The mid bar `$\mid$' indicates logical or.
Differences between regions are \uwave{underlined}.
}
\label{tab:2ljets_high}
\end{table}

@@

\begin{table}[tp]
\centering
\begin{tabular}{lccccc}
& $\njet$
& $\nbtag$
& $\metsig$
& $\mjj$
& $\ptjone$
\\[1em]
SR-Int
& $\geq 2$
& $\hphantom{\geq}~0$
& $12\textrm{--}15\textrm{--}18$
& $60\textrm{--}110$
& $> 60$
\\[0.5em]
\: VR-Int
& $\geq 2$
& $\hphantom{\geq}~0$
& $12\textrm{--}18$
& $60\textrm{--}110$
& $\uwave{< 60}$
\\[1em]
CR-VZ
& $\geq 2$
& $\hphantom{\geq}~0$
& $12\textrm{--}18$
& $\uwave{20\textrm{--}60 \mid 60\textrm{--}110}$
& $\uwave{\hphantom{< 60}}$
\\[0.5em]
CR-tt
& $\geq 2$
& $\uwave{\geq 1}$
& $\uwave{9\textrm{--}12}$
& $\uwave{20}$
& $> 60$
\end{tabular}
\\[1em]
Common: Pre-selection,
$\njet \geq 2$,
$\mll \in 81\textrm{--}101$, and
$\mttwoll > 80$.
\caption[
Intermediate region definitions in the $\twoljets$-electroweak analysis
]{%
Intermediate region definitions in the $\twoljets$-electroweak analysis.
En-dashes `$a\textrm{--}b$' indicate open intervals $(a, b)$.
Concatenated intervals `$a\textrm{--}b\textrm{--}c$' indicate binning
with boundaries at $a$, $b$, and $c$.
The mid bar `$\mid$' indicates logical or.
Differences between regions are \uwave{underlined}.
}
\label{tab:2ljets_int}
\end{table}

@@

\begin{table}[tp]
\centering
\begin{tabular}{lcccccccc}
& $\metsig$
& $\mjj$
& $\mttwoll$
& $\rll$
& $\dphillmet$
\\[1em]
SR-Low
& $6\textrm{--}9\textrm{--}12$
& $60\textrm{--}110$
& $> 80$
& $< 1$
&
\\[0.5em]
\: VR-Low
& $6\textrm{--}12$
& $60\textrm{--}110$
& $>80$
& $\uwave{1\textrm{--}1.4}$
&
\\[1em]
SR-Low-2
& $6\textrm{--}9$
& $60\textrm{--}110$
& $< 80$
& $< 1.6$
& $< 0.6$
\\[0.5em]
\: VR-Low-2
& $6\textrm{--}9$
& $\uwave{20\textrm{--}60 \mid 60\textrm{--}110}$
& $< 80$
& $< 1.6$
& $< 0.6$
\\[1em]
CR-Z
& $6\textrm{--}9$
& $\uwave{20\textrm{--}60 \mid 60\textrm{--}110}$
& $> 80$
& $\uwave{\hphantom{< 1.6}}$
& $\uwave{\hphantom{< 0.6}}$
\end{tabular}
\\[1em]
Common: Pre-selection,
$\njet = 2$,
$\nbtag = 0$, and
$\mll \in 81\textrm{--}101$.
\caption[
Low region definitions in the $\twoljets$-electroweak analysis
]{%
Low region definitions in the $\twoljets$-electroweak analysis.
En-dashes `$a\textrm{--}b$' indicate open intervals $(a, b)$.
Concatenated intervals `$a\textrm{--}b\textrm{--}c$' indicate binning
with boundaries at $a$, $b$, and $c$.
The mid bar `$\mid$' indicates logical or.
Differences between regions are \uwave{underlined}.
}
\label{tab:2ljets_low}
\end{table}

@@

\begin{table}[tp]
\centering
\begin{tabular}{lccccc}
& $\metsig$
& $\mll$
& $\mttwoll$
& $\ptjone$
& $\dphijmet$
\\[1em]
SR-OffShell
& $>9$
& $12\textrm{--}40\textrm{--}71$
& $>100$
& $>100$
& $>2$
\\[0.5em]
\: VR-OffShell
& $>9$
&  12--71
& $\uwave{80\textrm{--}100}$
& $> 100$
& $> 2$
\\[1em]
CR-DY
& $\uwave{6\textrm{--}9}$
& $12\textrm{--}71$
& $> 100$
& $\uwave{\hphantom{> 100}}$
& $\uwave{\hphantom{> 2}}$
\end{tabular}
\\[1em]
Common: Pre-selection,
$\njet \geq 2$, and
$\nbtag = 0$.
\caption[
Off-shell region definitions in the $\twoljets$-electroweak analysis
]{%
Off-shell region definitions in the $\twoljets$-electroweak analysis.
En-dashes `$a\textrm{--}b$' indicate open intervals $(a, b)$.
Concatenated intervals `$a\textrm{--}b\textrm{--}c$' indicate binning
with boundaries at $a$, $b$, and $c$.
The mid bar `$\mid$' indicates logical or.
Differences between regions are \uwave{underlined}.
}
\label{tab:2ljets_offshell}
\end{table}

@@

\begin{figure}[tp]
\centering
\includegraphics[width=0.9\textwidth]{figures/2ljets_low_mjj_SRLow_or_CRZ_mg5.pdf}
\caption[
The union of CR-Z and SR-Low with an alternative $\zjets$ simulation using
MadGraph
]{%
The union of CR-Z and SR-Low with an alternative $\zjets$ simulation using
MadGraph.
This sample has reduced statistical precision, decreased yields in the signal
region, and increased yields (which match data better) in the high-$\mjj$
overflow bin.
}
\label{fig:2ljets_low_sr_or_cr_region_alt}
\end{figure}

\begin{figure}[tp]
\centering
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_aux_CR_Z_EWKSR_Low_EWK_mjj_no_sr.png}
\caption{Fitted to control regions only}
\end{subfigure}
\hfill
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_aux_CR_Z_EWKSR_Low_EWK_mjj.pdf}
\caption{Fitted to control and signal regions}
\end{subfigure}
\caption[
Distribution of $\mjj$ in CR-Z and SR-Low with all systematic variations
]{%
Distribution of $\mjj$ in CR-Z and SR-Low with all systematic variations
(a) fitted to control regions, and (b) fitted to control and signal regions.
The arrows point in to the signal region, which shows a large peak in the
diboson background near $m(W)$.
Auxiliary materials to the paper~\cite{atlas2022searches} include (b), in which
the $\zjets$ background in SR-Low has been collapsed to fit the deficit.
Pre-fit yields are presented in Figures~\ref{fig:2ljets_low_sr_or_cr_region}
and~\ref{fig:2ljets_low_sr_or_cr_region_alt}.
}
\label{fig:2ljets_low_crz_pre_post}
\end{figure}

\begin{figure}[tp]
\centering
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_vrlow_met_Sign_VRLow.pdf}
\caption{Standard}
\end{subfigure}
\hfill
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_vrlow_met_Sign_VRLow_mg5.pdf}
\caption{Alternative}
\end{subfigure}
\caption[
Pre-fit yields in VR-Low with standard and alternative $\zjets$ simulations
]{%
Pre-fit yields in VR-Low with (a) standard and (b) alternative $\zjets$
simulations.
Errors are statistical.
}
\label{fig:2ljets_vrlow_alt}
\end{figure}

\begin{figure}[tp]
\centering
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_prefit_VR_Low_EWK_met_Sign_no_sr.png}
\caption{Fitted to control regions only}
\end{subfigure}
\hfill
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_postfit_VR_Low_EWK_met_Sign.pdf}
\caption{Fitted to control and signal regions}
\end{subfigure}
\caption[
Comparison of VR-Low before and after fitting to the signal regions
]{%
Comparison of VR-Low (a) before and (b) after fitting to the signal regions.
All systematic variations are included after fitting to the control regions.
The signal region deficit pulls $\zjets$ yields below data in the validation
region, whose likelihood is not included in the \heplikelihood.
}
\label{fig:2ljets_low_vrlow_pre_post}
\end{figure}

Figure~\ref{fig:2ljets_prepre}

\begin{figure}[tp]
\centering
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_prepre_met_Sign_VRpresel_2j_MCfakeslogY.pdf}
\caption{$\metsig$}
\end{subfigure}
\hfill
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_prepre_mt2leplsp_0_VRpresel_2j_MCfakeslogY.pdf}
\caption{$\mttwoll$}
\end{subfigure}
\caption[
Histograms in a very loose pre-selection like those inspected to validate
background modelling prior to designing the $\twoljets$ regions.
]{%
Histograms in a very loose pre-selection like those inspected to validate
background modelling prior to designing the $\twoljets$ regions.
This selection requires `Pre-selection' from Table~\ref{tab:2ljets_presel} and
$\njet \geq 2$.
Errors are statistical.
Each last bin contains overflow.
}
\label{fig:2ljets_prepre}
\end{figure}
